Data Prep: IUCN and AquaMaps

### 2016-02-11 data_explore/data_prep.Rmd
I think I have all the name matching issues worked out?

spp_am_v_iucn <- spp_all %>%
  filter(str_detect(spatial_source, 'iucn') & !is.na(am_sid)) %>%
  filter(!is.na(id_no)) %>%
  unique()
# length(unique(spp_am_v_iucn$am_sid)); length(unique(spp_am_v_iucn$iucn_sid))
### NOTE: 2377 unique scientific names; but 2315 unique am_sid and 2280 unique iucn_sid.
x <- spp_am_v_iucn[duplicated(spp_am_v_iucn$am_sid)   | duplicated(spp_am_v_iucn$am_sid,   fromLast = TRUE), ] %>%
  select(sciname, iucn_sid, am_sid, id_no, spatial_source, name_verified)
y <- spp_am_v_iucn[duplicated(spp_am_v_iucn$iucn_sid) | duplicated(spp_am_v_iucn$iucn_sid, fromLast = TRUE), ] %>%
  select(sciname, iucn_sid, am_sid, id_no, spatial_source, name_verified)

write_csv(spp_am_v_iucn, file.path(dir_data, 'spp_am_v_iucn.csv'))
```

@@

data_file <- file.path(dir_data, 'spp_list_w_area_all.csv')
reload <- TRUE
if (!file.exists(data_file) | reload) {
  ### species info list - scinames, IUCN species ID, AM species ID, category etc
  spp_list_base <- read.csv(file.path(dir_data, 'spp_am_v_iucn.csv'),
                            stringsAsFactors = FALSE)

>>>>

spp_am_v_iucn <- spp_all %>%
  filter(str_detect(spatial_source, 'iucn') & !is.na(am_sid)) %>%
  filter(!is.na(id_no)) %>%
  filter(!str_detect(spp_group, 'MARINEFISH')) %>%
  unique()
# length(unique(spp_am_v_iucn$am_sid)); length(unique(spp_am_v_iucn$iucn_sid))
### NOTE: 2345 unique scientific names; but 2283 unique am_sid and 2249 unique iucn_sid.
### Some unique species (as identified by am_sid and iucn_sid) have multiple
### scinames.  At this point, not really important what the sciname is?
spp_am_v_iucn1 <- spp_am_v_iucn %>%
  group_by(am_sid, iucn_sid) %>%
  mutate(dupes = n() - 1,
         first_instance = sciname == first(sciname)) %>%
  filter(!(dupes > 0 & !first_instance)) %>%
  select(-dupes, -first_instance) %>%
  ungroup()
# length(unique(spp_am_v_iucn1$am_sid)); length(unique(spp_am_v_iucn1$iucn_sid))

### What species are represented by the duplicated IUCN ID numbers?  These
### are species that IUCN experts lumped together (via synonyms etc) 
### but are treated as separate by AquaMaps (the reverse does not seem
### to happen)...  There are 64 AM species IDs and only 30 IUCN species IDs.  
### How to treat in the mapping?
### * lump AM species together and plot against a single IUCN species map?
###   That would occur in the area determining function - group by iucn_sid
###   and map all am_sids against that iucn_sid
x <- spp_am_v_iucn1 %>%
  group_by(iucn_sid) %>%
  filter(n() > 1)
# length(unique(x$am_sid)); length(unique(x$iucn_sid))

write_csv(spp_am_v_iucn1, file.path(dir_data, 'spp_am_v_iucn.csv'))
```

@@

data_file <- file.path(dir_data, 'spp_list_w_area_all.csv')
reload <- TRUE
if (!file.exists(data_file) | reload) {
  ### species info list - scinames, IUCN species ID, AM species ID, category etc
  spp_list_base <- read_csv(file.path(dir_data, 'spp_am_v_iucn.csv'))
